Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-01-24 ms.tex
clean up

\begin{abstract}
We present full-sky, $6.1'$ resolution maps of dust optical depth and 
temperature derived by fitting the \cite{FDS99} two-component dust emission 
model to \PLANCK~217, 353, 545, and 857 GHz, along with \cite{SFD} 
\IRAS~100$\mu$m data. These maps serve as an important alternative to and 
point of comparison for other dust emission models, especially the single 
modified blackbody model in which both the emissivity power law index and dust 
temperature vary continuously. We also expect the derived optical depth to 
provide valuable cross-checks for other dust-column related data products, 
specifically the \cite{SFD} map, which assumed a single modified blackbody 
with $\nu^2$ emissivity and included a temperature map of inferior 
$\sim$$1.3^{\circ}$ resolution. We compare our best-fit two-component spectral 
energy distributions to those of the \cite{planckdust} single-component 
parametrization.
%MENTION USE IN MAKING IR FOREGROUND PREDICTIONS
%mention more explicitly the enhanced temperature resolution relative to SFD??
%Our optical depth map will also provide a useful reference for dust maps 
%based on stellar colors rather than infrared emission.
\end{abstract}

@@

To incorporate measurements on the Wien side of the dust emission spectrum, 
we include 100$\mu$m data in our SED fits. In particular, we use the SFD 
reprocessing of \IRAS~100$\mu$m, which we will refer to as \verb|i100|, and at 
times by frequency as 3000 GHz. The \verb|i100| map has angular resolution of 
$6.1'$, and was constructed so as to contain only thermal 
emission from Galactic dust, with compact sources and zodiacal light removed, 
and its zero level tied to H\,\textsc{i}. We use the \verb|i100| map as is, without any 
custom modifications.
%maybe clarify that throughout we use SFD i100 totally as-is, with no
% customization

%list other %important characteristics of i100 e.g. that it has been 
%zodi-corrected and relies on dirbe on scales larger than ???

>>>>

\begin{abstract}
We present full-sky, $6.1'$ resolution maps of dust optical depth and 
temperature derived by fitting the \cite{FDS99} two-component dust emission 
model to \PLANCK~217, 353, 545, and 857 GHz, along with  \IRAS~100$\mu$m data. 
These maps serve as an important alternative to and point of comparison for 
other dust emission models, especially the single modified blackbody model in 
which both the emissivity power law index and dust temperature vary 
continuously. We also expect the derived optical depth to provide valuable 
cross-checks for other dust-column related data products, specifically the 
\cite{SFD} map, which assumed a single modified blackbody with $\nu^2$ 
emissivity and included a temperature map of inferior $\sim$$1.3^{\circ}$ 
resolution. We compare our best-fit two-component spectral energy distributions
to those of the \cite{planckdust} single-component parametrization.
%MENTION USE IN MAKING IR FOREGROUND PREDICTIONS
%mention more explicitly the enhanced temperature resolution relative to SFD??
%Our optical depth map will also provide a useful reference for dust maps 
%based on stellar colors rather than infrared emission.
\end{abstract}

@@

To incorporate measurements on the Wien side of the dust emission spectrum, 
we include 100$\mu$m data in our SED fits. In particular, we use the 
\citet[henceforth SFD]{SFD} reprocessing of \IRAS~100$\mu$m, which we will 
refer to as \verb|i100|, and at times by frequency as 3000 GHz. The \verb|i100|
 map has angular resolution of $6.1'$, and was constructed so as to contain 
only thermal emission from Galactic dust, with compact sources and zodiacal 
light removed, and its zero level tied to H\,\textsc{i}. We use the \verb|i100|
map as is, without any custom modifications.
%maybe clarify that throughout we use SFD i100 totally as-is, with no
% customization

%list other %important characteristics of i100 e.g. that it has been 
%zodi-corrected and relies on dirbe on s
